Spatial Analysis

### 2021-06-28 Scripts/spatial_analisis.Rmd
grid eez df for pens.

# Remove Pennsylvania from sf
grid_eez_df <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>% 
  filter(state != "pennsylvania")

# Make sure no Penn.
unique(grid_eez_df$state)

# over write sf
write_sf(grid_eez_df, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))

@@

>>>>

# Remove Pennsylvania from sf
grid_eez_sf <-  st_read("/Volumes/Enterprise/Data/AcrossBoundaries/Data/Spatial/grid_sf/grid_eez_sf.shp") %>% 
  filter(state != "pennsylvania")

# Make sure no Penn.
unique(grid_eez_sf$state)

# over write sf
write_sf(grid_eez_sf, paste0(my_path("D", "Spatial"),"grid_eez_sf.shp"))

@@

# Now save it as a DF too

grid_eez_df <- as.data.frame(grid_eez_sf) %>%
  select(state,index) %>% 
  left_join(ne_grid, 
            by = "index")

write_csv(grid_eez_df, paste0(my_path("R", "Partial"),"grid_eez_df.csv"))
